\papertitle

### 2012-10-12 manuscript.tex
Added Pose Estimation/Motion Model

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}

@@

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on the H$^2$Bird using 
a particle filter-based motion tracking algorithm. This pose estimate is 
the feedback input to the cooperative visual servoing feedback loop (Sec. \ref{sec:visual_servoing_concept}).

We limit our pose estimation approach to monocular two-dimensional object 
tracking in pixel-space. This allows us to perform high-rate video tracking 
using the modest computational resources available on the ground station, 
and similarly millirobotic ground vehicles.

~\cite{thrun2005probabilistic}

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
%TODO ryan

>>>>

%----------------------------------------------------------------------------%
% PACKAGES
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{amsmath}

\newlength\eqnindent
\newlength\eqncolwid
\newcommand\eqntext[2][0pt]{%
  \setlength\parindent{0pt}%
      \setlength\eqnindent{#1}\setlength\eqncolwid{\linewidth}%
  \setlength\eqncolwid{\dimexpr\linewidth-\eqnindent}%
  \hspace*{\eqnindent}\parbox{\eqncolwid}{#2}%
}

@@

%----------------------------------------------------------------------------%
\subsection{Ground Station Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on 
H$^2$Bird using a particle filter-based motion tracking algorithm. This pose 
estimate is the feedback input to the cooperative visual servoing feedback 
loop (Sec. \ref{sec:visual_servoing_concept}). We limit our pose estimation 
approach to monocular two-dimensional object tracking in pixel space. This 
allows us to perform real-time video tracking using the modest computational 
resources available on the ground station, and similarly millirobotic ground 
vehicles.

Our pose estimation algorithm tracks H$^2$Bird motion in the frame using a 
particle filter~\cite[96-114]{thrun2005probabilistic}. We initialze particles 
uniformly across the frame. To improve numerical stability, we  normalize the 
weights of all particles on each iteration, and only resample the particle 
population when the mean particle weight falls below a pre-determined 
threshold.

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this paper used a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

%............................................................................%
\subsubsection{Emission Model}

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
